Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation

### 2013-08-08 writedown/npt-neq/alanine.tex
start adding orientational order parameter

% \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
\documentclass[aip,jcp,a4paper,preprint,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\subsection{System settings and simulation protocol}
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[]{fig.ala/field.dipole/fig-field-dipol-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The magnitude of the external electric field, and the
    $x$-component of the dipole moment of the alanine molecule as a
    function of time. The dashed line presents the strengths of the
    external electric field, while the solid line presents the dipole
    moments. }
  \label{fig:tmp3}
\end{figure}

In this section,
we want to study the nonequilibrium properties of an alanine dipeptide
under a constant EF. At time $t=0$~ps, the system
has been fully equilibriated without any electric field. From $t=0$ to
$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
after $t=t_{\textrm{init}}$, the field is kept constant at
$E_{\infty}$. In Fig.~\ref{fig:tmp3}, the dashed line shows the 
cases considered in this work: $t_{\textrm{init}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of this field is arbitrarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction (see also Fig.~\ref{fig:tmp3} for
the vanished initial dipole moment), applying the electric along $x$-axis is
not biased.
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
MD simulation, if not stated otherwise.
% They server as starting point of the branching
% trajectories.
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an obviously effect on the
dynamics of the system.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
  \caption{The population of metastable states of the alanine dipeptide.
    Left: the
    equilibrium state at $t=0$~\textsf{ps}. Right: The new equilibrium
    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
    constant electric field 1~V/nm. The darker color
    indicates larger population on the Ramachandran histogram.}
  \label{fig:tmp4}
\end{figure}

@@

>>>>

% \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
\documentclass[a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\subsection{System settings and simulation protocol}
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
  % \\
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
  \caption{The
    $x$-component of the dipole moment, and the orientational order parameter
    of the alanine molecule as a
    function of time. The dashed line presents the strengths of the
    external electric field, while the solid line presents the dipole
    moments. }
  \label{fig:tmp3}
\end{figure}

In this section,
we want to study the nonequilibrium properties of an alanine dipeptide
under a constant EF. At time $t=0$~ps, the system
has been fully equilibriated without any electric field. From $t=0$ to
$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
after $t=t_{\textrm{init}}$, the field is kept constant at
$E_{\infty}$.  In this work we consider $t_{\textrm{init}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of this field is arbitrarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction, applying the electric along $x$-axis is
not biased.
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
MD simulation, if not stated otherwise.
% They server as starting point of the branching
% trajectories.
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an obviously effect on the
dynamics of the system.

%  (see also Fig.~\ref{fig:tmp3} for
%  the vanished initial dipole moment)

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
  \caption{The population of metastable states of the alanine dipeptide.
    (a): the
    equilibrium state at $t=0$~\textsf{ps}. (b): The new equilibrium
    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
    constant electric field 1~V/nm. The darker color
    indicates larger population on the Ramachandran histogram.}
  \label{fig:tmp4}
\end{figure}

@@

The D-NEMD method. The design of the nonequilibrium thermostating.

Time scales discovered in the constant EF case.

The discover of the directional probability flux introduced by the
oscillating EF.

Comment on the force field. cite A.Mey's paper.

Comment on the real life-strength and frequency of the EF, if it is
possible in experiment. such a strong field may distroy the molecule.

Comment on the limitation of the non-polarizable model.
